R for Clinical Study Reports and Submission

### 2021-09-15 tlf-baseline.Rmd
update baseline table

There is many R packages that can efficiently summarize baseline information.
The [`table1`](https://github.com/benjaminrich/table1) R package is one of them.

@@

For simplicity, we only analyze `SEX`, `AGE` and `RACE` in this example
using the `table1` R package. 
More details of the `table` R package can be found in the package
[vignettes](https://benjaminrich.github.io/table1/vignettes/table1-examples.html).

The `table1` R package directly create an HTML report.

@@

The code below transfer the output into a dataframe 
that only contain ASCII character 
recommended by regulatory agencies. 
`tbl_base` is used as input for `r2rtf` to create final report.

@@

We start to define the format of the output. We highlight items that 
are not discussed in previous discussion.

`text_indent_first` and `test_indent_left` are used to control the indent
space of text. They are helpful when you need to control the white space 
of a long sentence. For example, "AMERICAN INDIAN OR ALASKA NATIVE" 
in the table.

@@

In conclusion, the procedure to generate demographic and baseline characteristics table is summarized as follows.

- Step 1: Read the data set.
- Step 2: Use `table1::table1()` to get the baseline characteristics table.
- Step 3: Transfer the output in Step 2 into a data frame that only contains ASCII character.
- Step 4: Define the format of the rtf table by using R package `r2rtf`.

>>>>

There are many R packages that can efficiently summarize baseline
information. The [`table1`](https://github.com/benjaminrich/table1) R
package is one of them.

@@

For simplicity, we only analyze `SEX`, `AGE` and, `RACE` in this example
using the `table1` R package. More details of the `table` R package can
be found in the package
[vignettes](https://benjaminrich.github.io/table1/vignettes/table1-examples.html).

The `table1` R package directly creates an HTML report.

@@

The code below transfer the output into a data frame that only contain
ASCII character recommended by regulatory agencies. `tbl_base` is used
as input for `r2rtf` to create a final report.

@@

We start to define the format of the output. We highlight items that are
not discussed in the previous discussion.

The `text_indent_first` and `test_indent_left` arguments are used to
control the indent space of the text. They are helpful when you need to
control the white space of a long sentence. For example, "AMERICAN
INDIAN OR ALASKA NATIVE" in the table.

@@

The procedure to generate a baseline characteristics table can be
summarized as follow:

-   Step 1: Read the data set.
-   Step 2: Use `table1::table1()` to get the baseline characteristics
    table.
-   Step 3: Transfer the output in Step 2 into a data frame that only
    contains ASCII characters.
-   Step 4: Define the format of the rtf table by using R package
    `r2rtf`.
